Using Distributed Information Stores for Patient-Clinician Health Data Sharing

### 2013-01-16 patient-clinician-workshop/pccworkshop.tex
Nigel bio

%\section{Biographies}

>>>>

\section{Biographies}

\subsection{Daniel A. Smith and Max Van Kleek}

\subsection{Nigel R. Shadbolt}

Nigel Shadbolt (FBCS FREng) is Professor of Artificial Intelligence and Head of the Web and Internet Science Group, Electronics and Computer Science, University of Southampton. He is the Chairman and Co-Founder of the Open Data Institute, Director of the Web Science Trust, and of the Web Foundation. In 2009 the Prime Minister appointed him and Sir Tim Berners-Lee as Information Advisors to transform access to Public Sector Information, leading to the highly acclaimed data.gov.uk. He is a member of the Public Sector Transparency Board, overseeing Open Data releases across the public sector. He is Chair of the UK Government’s midata programme, which seeks to empower consumers by releasing their data back to them.

\section{Key Technology: WebBox}

WebBox is...
